weight_analyses

### 2022-10-14 smelt_2019_winterspring/Diet.Rmd
add in color palette for final plot
updated dataframe name

# bring in data
```{r}
diet <- read_csv("smelt_2019_winterspring/data_raw/DSM Cage Diets 2019 update_taxa.csv")
diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

@@

>>>>

# bring in data
```{r}
diet <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_diet_data.csv")
diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

@@

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
